---
title: "Project Forecasting"
author: "Fabian Schmidt"
date: "12/01/2020"
output: html_document
---
```{r}
rm( list=ls() )

library(tidyverse)

getCurrentFileLocation <-  function() {
  this_file <- commandArgs() %>% 
    tibble::enframe(name = NULL) %>%
    tidyr::separate(col=value, into=c("key", "value"), sep="=", fill='right') %>%
    dplyr::filter(key == "--file") %>%
    dplyr::pull(value)
  if (length(this_file)==0) {
    this_file <- rstudioapi::getSourceEditorContext()$path
  }
  return(dirname(this_file))
}

file_dir <- getCurrentFileLocation()
setwd(file_dir)

source('./utilities.R')
```

Read the data
```{r}
china <- read.csv("../data/CHIEPUINDXM.csv")
us <- read.csv("../data/USEPUINDXD.csv")
```

Construct returns dates
```{r}
datesus <- as.Date(us$DATE)
datesch <- as.Date(china$DATE)
```

 Get the adjusted epu.us series and plot it
```{r}
epu.us <- us$USEPUINDXD;
myplot( datesus , epu.us)
```

 Get the adjusted epu.china series and plot it
```{r}
epu.ch <- china$CHIEPUINDXM;
myplot( datesch , epu.ch)
```

 Construct the delta.epu.us and log.epu.us series for us, plot it and produce a pdf
```{r}
T <- length(datesus)

delta.epu.us <- diff( log( epu.us ) ) * 100

log.epu.us <- log(epu.us)
log.epu.us <- log.epu.us[2:T] # Reassign length due to loss of one obs in diff

myplot( datesus[2:T] , delta.epu.us , col='red2' )
abline(h=0 , lwd=2)

pdf(file='../images/epu_us.pdf',width=7,height=5)
myplot( datesus[2:T], delta.epu.us, col='red2' )
abline(h=0 , lwd=2)
dev.off() 

myplot( datesus[2:T] , log.epu.us , col='red2' )
abline(h=0 , lwd=2)

pdf(file='../images/log_epu_us.pdf',width=7,height=5)
myplot( datesus[2:T], log.epu.us, col='red2' )
abline(h=0 , lwd=2)
dev.off() 
```

 Pack dates and delta.epu.us in a data frame and write it to disk
```{r}
data.us <- cbind.data.frame(datesus[2:T],delta.epu.us, log.epu.us)
write.table(data.us, '../data/delta_epu_us.csv',sep=' ', row.names=FALSE,col.names=FALSE)
```

 Construct the delta.epu.ch and log.epu.ch series for us, plot it and produce a pdf
```{r}
T <- length(datesch)

delta.epu.ch <- diff( log( epu.ch ) ) * 100

log.epu.ch <- log(epu.ch)
log.epu.ch <- log.epu.ch[2:T] # Reassign length due to loss of one obs in diff

myplot( datesch[2:T] , delta.epu.ch , col='red2' )
abline(h=0 , lwd=2)

pdf(file='../images/epu_ch.pdf',width=7,height=5)
myplot( datesch[2:T], delta.epu.ch, col='red2' )
abline(h=0 , lwd=2)
dev.off() 

myplot( datesch[2:T] , log.epu.ch , col='red2' )
abline(h=0 , lwd=2)

pdf(file='../images/log_epu_ch.pdf',width=7,height=5)
myplot( datesch[2:T], log.epu.ch, col='red2' )
abline(h=0 , lwd=2)
dev.off()
```

 Pack dates and delta.epu.ch in a data frame and write it to disk
```{r}
data.ch <- cbind.data.frame(datesch[2:T], delta.epu.ch, log.epu.ch)
write.table(data.ch, '../data/delta_epu_ch.csv', sep=' ', row.names=FALSE,col.names=FALSE)
```